NumPy---Array Programming in Python

### 2020-01-16 body.tex
Minor edits / comments from Ralf

To facilitate \emph{interoperability}, the NumPy team is defining so-called
``protocols'' (or contracts of operation), that allow for these arrays to be
passed to NumPy functions.
NumPy, in turn, dispatches operations to the originating library, as required.
% FIXME: expand to 3 or more sentences discussing current efforts and
% issues with those, how did adoption go, what is being done next
%\url{https://numpy.org/neps/nep-0037-array-module.html}
Early versions of these protocols have been successfully deployed.

>>>>

To facilitate \emph{interoperability}, the NumPy team has designed
``protocols'' (or contracts of operation), that allow for these arrays to be
passed to NumPy functions.
NumPy, in turn, dispatches operations to the originating library, as required.
% FIXME: expand to 3 or more sentences discussing current efforts and
% issues with those, how did adoption go, what is being done next
%\url{https://numpy.org/neps/nep-0037-array-module.html}
Versions of these protocols have been successfully deployed.
% Ralf: Could you provide some proof of effectiveness, e.g., "This has made it
% possible to create distributed GPU arrays, enabling .... [find a reference to
% work by Peter Entschev]".
